---
title: "Assignment 7: Intro Survey Data Analysis"
output: html_document
---

Michael Lew - Summary statistics, HTML page

Jacob Burke - Charting function 2

Jon Jewik - Charting function 1

Kush Gupta - Charting function 2

Info498f

Assignment 7: Collaborative Coding

```{r eval=TRUE, echo=FALSE, message=FALSE}
library(plotly)
library(dplyr)

#Read in data (the file in data/ wasn't made public so that won't work)
data <- read.csv("https://raw.githubusercontent.com/INFO-498F/a7-survey-data/master/intro_survey_data.csv")

#____________________________________
#1) Summary statistics
source("scripts/summary_statistics.R")
sl <- summarise_data(data)

# Expected value of summary_list:
#   numbers indicate degree, like class_standing1 indicates Freshman, 2=sophomore, 3=junior, 4=senior,
#   programming_experience1 = no experience, 2=some experience, 3=moderate experience, 4=lots of experience

#        students_enrolled           class_standing1           class_standing2 
#                     "81"                      "15"                      "41" 
#          class_standing3           class_standing4   programming_experience1 
#                     "18"                       "7"                       "3" 
#  programming_experience2   programming_experience3   programming_experience4 
#                     "29"                      "46"                       "3" 
#  total_countries_visited average_countries_visited 
#                    "434"                    "5.36" 

# Here's a link to reference to getting stuff from a list:
# http://www.r-tutor.com/r-introduction/list/named-list-members

```
#Summary paragraph about the Info Survey

Of `r sl$students_enrolled` people enrolled in INFO498F, `r sl$class_standing1` were Freshmen, `r sl$class_standing2` were Sophomores, `r sl$class_standing3` were Juniors, and `r sl$class_standing4` were Seniors.

`r sl$programming_experience1` enrolled students said that they had never coded before, `r sl$programming_experience2` said they had only experimented with code, `r sl$programming_experience3` had a moderate amount of programming experience, and `r sl$programming_experience4` had lots of programming experience.

All students put together had visited a total of `r sl$total_countries_visited` countries (not exclusive); each student has visited an average of `r sl$average_countries_visited` countries.

#Scatter Plot & Bar Plot

```{r eval=TRUE, echo=FALSE, message=FALSE}

#____________________________________
#2) Charting function 1

# Makes a scatter plot for number of countries visited
source("scripts/chart1.R")
Scatter_Plot(data)

#____________________________________
#3) Charting function 2

# Bar plot for students in each class standing
source("scripts/chart2.R")
Bar_Plot(data)



```