Jacob Burke, Jon Jewik, Kush Gupta, Michael Lew

Info498f

Assignment 7: Collaborative Coding

---
title: "Assignment 7: Intro Survey Data Analysis"
output: html_document
---










[intro paragraph goes here, tell what the stuff below does]











```{r eval=TRUE, echo=FALSE, message=FALSE}
library(jsonlite)
library(plotly)
library(dplyr)

#Read in data (the file in data/ wasn't made public so that won't work)
data <- read.csv("https://raw.githubusercontent.com/INFO-498F/a7-survey-data/master/intro_survey_data.csv")
setwd("C:/Users/jonje/documents/info498f/a7-collaborative-coding")

#____________________________________
#1) Summary statistics
source("scripts/summary_statistics.R")
sl <- summarise_data(data)

# Expected value of summary_list:
#   numbers indicate degree, like class_standing1 indicates Freshman, 2=sophomore, 3=junior, 4=senior,
#   programming_experience1 = no experience, 2=some experience, 3=moderate experience, 4=lots of experience

#        students_enrolled           class_standing1           class_standing2 
#                     "81"                      "15"                      "41" 
#          class_standing3           class_standing4   programming_experience1 
#                     "18"                       "7"                       "3" 
#  programming_experience2   programming_experience3   programming_experience4 
#                     "29"                      "46"                       "3" 
#  total_countries_visited average_countries_visited 
#                    "434"                    "5.36" 

# Here's a link to reference to getting stuff from a list:
# http://www.r-tutor.com/r-introduction/list/named-list-members

```
#Summary paragraph about the Info Survey

Of `r sl$students_enrolled` people enrolled in INFO498F, `r sl$class_standing1` were Freshmen, `r sl$class_standing2` were Sophomores, `r sl$class_standing3` were Juniors, and `r sl$class_standing4` were Seniors.

`r sl$programming_experience1` enrolled students said that they had never coded before, `r sl$programming_experience2` said they had only experimented with code, `r sl$programming_experience3` had a moderate amount of programming experience, and `r sl$programming_experience4` had lots of programming experience.

All students put together had visited a total of `r sl$total_countries_visited` countries (not exclusive); each student has visited an average of `r sl$average_countries_visited` countries.

```{r eval=TRUE, echo=FALSE, message=FALSE}

#____________________________________
#2) Charting function 1

function1 <- source("C:/Users/jonje/documents/info498f/a7-collaborative-coding/scripts/chart1.R")
function1(data)



#____________________________________
#3) Charting function 2

# [insert source("scripts/filename") here]
# [function from that file goes here]

# Grouped Bar Plot
# Simple Bar Plot 
counts <- table(data$What.is.your.current.class.standing.)
barplot(counts, main="Class Standing in Info 498f", 
  	xlab="Class Standing", col=c("darkblue","red", "yellow", "green")



```