# Assignment 7: Collaborative Coding

----

### INFO 498F

##### Team members:

    - Jacob Burke (Charting Function 2)
    - Jon Jewik (Charting Function 1)
    - Kush Gupta (index.Rmd file)
    - Michael Lew (Summary Statistics)

```{r, echo=FALSE, message=FALSE} 

# Including Libraries
library(plotly)
library(dplyr)

# Including the summary statistics script
source('scripts/summary_statistics.R')

# Reading data (in the form of a data.frame) from the source
data <- read.csv("https://raw.githubusercontent.com/INFO-498F/a7-survey-data/master/intro_survey_data.csv")

# Summarising the data
summary <- summarise_data(data)

```

### Summary for INFO 498F Survey

---

Out of the `r summary[['students_enrolled']]` students enrolled into INFO 498F, `r summary[['class_standing1']]` were Freshmen, `r summary[['class_standing2']]` were Sophomores, `r summary[['class_standing3']]` were Juniors, and `r summary[['class_standing4']]` were Seniors. 

When it comes to Programming experience, `r summary[['programming_experience1']]` students say they have no programming experience, `r summary[['programming_experience2']]` students say they have experimented a bit with simple programing, `r summary[['programming_experience3']]` students say they have moderate experience with some scripting language (Python, R, JavaScript, Java, etc.), and `r summary[['programming_experience4']]` students say they have a lot of experience with a scripting language.

All students together have visited `r summary[['total_countries_visited']]` countries, which is about `r summary[['average_countries_visited']]` countries per student on an average.


### Chart 1

---
```{r, echo=FALSE, message=FALSE}
# Rendering the first chart 

# source('scripts/chart1.R')
# scatter_plot(data)

```

### Chart 2

---
```{r, echo=FALSE, message=FALSE}
# Rendering the second chart

# source('scripts/chart2.R')
# bar_plot(data)
```